### 2017-11-21 Docs/Thesis/docs/chapter6.tex
update on ch6

Starting with some concepts and ideias, we started definin our goals, and to do so, a task list. The concepts and the task lists were organized on "Working Plan" documents. These tasks lists covered the whole process, and included reserch, study of new subjects, implementation and testing. Next, search in the literatue the state of things, related works and some gaps for inovation. At this point we defined the concepts of our traffic generator according to gaps the state of things we find in the literature. Then we create an architecture model using UML, defining the software components, classes and sequence diagrams. This initial step was crucial, since on later stages, changes on the architecture design are much more dificult. In fact, some ponctual changes such as directory structure and new classes are inevitable. But structural changes are impracticable. At this point we implemented a simplistic prototype, and validate it\footnote{In the appendix ~\ref{ap:publications}, this prototype is validated in the article "Towards a Flexible and Extensible Framework for Realistic Traffic Generation on Emerging Networking Scenarios"}.

After this we serch for more sollutions and methodologies that could be applied to solve or problems and improove the performance of ou prototype. In this procedure we researched many topics that at end didn't fit to our intentions, such as Machine Learning and Neural Networks. But others such as Linear regression, maximum likelihood, and information criterions (BIC/AIC) were indeed sactisfatory. Again, we planned a methodology, a procedure, and validate these ideais, as prototypes. Here the seed for the first part of the chapter ~\ref{ch:modeling-evaluation} and the article "Using BIC and AIC for Ethernet traffic model selection. Is it worth?"(at appendix ~\ref{ap:publications}. Than we reseach for more related works to  gain insights and find platforms and lybraries able to fulfill our requirements. In this step we designed our algorithms presented on chapter ~\ref{ch:modeling-evaluation}, and choosed the APIs, packages and lybraries, such as Armadillo\cite{armadillo}, a C++ linear algebra lybrary. Many ideas we used to conceive our ideas were inspired on previous works and sollutions, such as Harpoon\cite{harpoon-validation}, sourcesOnoff \cite{sourcesonoff-paper} and LegoTG\cite{legotg-paper}. This procedure continued by incremental upgrades, until we arrived on the version presented on the chapter ~\ref{ch:validation}.

In the chapter ~\ref{ch:modeling-evaluation} we achieve a major contribution of our work, that is show that the information criterias AIC and BIC are efficient analyctial methodos for select models for inter-packet times. Both are able infer a good model, even evaluated according different types of metrics, without any type of simulation. Also we show evidence that for Ethernet traffic of data, choosing AIC and BIC make almost no difference. As far as is our knowleadge, this is the most complete study on the use of AIC and BIC on inter-packet times modelling of Ethernet traffic.

At the end, we were able to implement a functional implementation of solution proposed in the chapter ~\ref{ch:introduction}. Our main contrubution here is the development of a traffc generator tool that at the same time is able to provide realistic synthetic traffic, and its modelling framework is extensible for most of the traffic generation lybraries and tools. In fact, our current implementations use tow very distinct packet-crafters: \textit{libtins}, a C++ library designed for the implementation of sniffers and traffic generators, and Iperf, a traffic generator commonly used to measure bandwidth.

Out tests performed on the chapter ~\ref{ch:validation} intend to focous on packet-level, flow-level and scalling metrics, as we state on chapter ~\ref{ch:ch:literature-review}. The results were notably good at the flow level. SIMITAR were able to replicate the flow-cumulative distribution with high acurracy, and with \textit{libtins}, the number of flows as well. The number of flows were larger, because it establishes aditional connections for signaling and statistics control. On scalling and packet matrics, the results still have to be improved. Iperf as the traffic generator tool, still being limited, has prooved to be efficient on replication the scalling characteristics for the Skype traffic. Since it estrablishes socket connections to generate the traffic, we believe that this fact make it and acurate on replication traffic from applications.

Finally, we created a list of improovments and future works, aiming the improovment of perfomance on processing time, and packet generaration; and the methods to improove the realism of the traffic generated. In the is we believe to overcome the current limitations.

>>>>

We started defining our goals creating a task list, formalizing it on "Working Plan" documents. These tasks lists covered the whole process and included research, the study of new subjects, implementation, and testing. Next, search on the literature the state of things, related works and points for innovation. At this point, we defined the concepts of our traffic generator. We create an architecture model using UML, defining the software components, classes and sequence diagrams. This initial step was crucial since, in later stages, changes in the architecture design are much more difficult. In fact, some small changes such as directory structure and new classes are inevitable. But structural changes are impracticable. At this point we implemented a simplistic prototype, and validate it\footnote{In the appendix ~\ref{ap:publications}, this prototype is validated in the article "Towards a Flexible and Extensible Framework for Realistic Traffic Generation on Emerging Networking Scenarios"}.

After this, we search for more solutions and methodologies that could be applied to solve our problems and improve the performance of our prototype. In this procedure, we researched many topics that at the end didn't fit our intentions, such as Machine Learning and Neural Networks. But others such as Linear regression, maximum likelihood, and information criterions (BIC/AIC) were indeed satisfactory. Again, we planned a methodology, procedure, and validate these ideas, as prototypes. Here the seed for the first part of the chapter ~\ref{ch:modeling-evaluation} and the article "Using BIC and AIC for Ethernet traffic model selection. Is it worth?" (in the appendix ~\ref{ap:publications}). Then we research for more related works to gain insights and find platforms and libraries able to fulfill our requirements. In this step, we designed our algorithms presented in chapter ~\ref{ch:modeling-evaluation}, and chose the APIs, packages, and libraries, such as Armadillo\cite{armadillo}, a C++ linear algebra library. Many ideas we used to conceive our ideas were inspired by previous works and solutions, such as Harpoon\cite{harpoon-validation}, sourcesOnoff \cite{sourcesonoff-paper} and LegoTG\cite{legotg-paper}. This procedure continued with incremental upgrades until we arrived on the version presented on the chapter ~\ref{ch:validation}.

In the chapter ~\ref{ch:modeling-evaluation} we achieve a significant contribution of our work, which shows that the information criteria AIC and BIC are efficient analytical methods for select models for inter-packet times. Both can infer a good model, even evaluated according to different types of metrics, without any simulation. Also, we show evidence that for Ethernet traffic of data, choosing AIC and BIC make almost no difference. As far as is our knowledge, this is a complete study on the use of AIC and BIC on inter-packet times modeling of Ethernet traffic.

In the end, we were able to implement a functional implementation of the solution proposed in the chapter ~\ref{ch:introduction}. Our main contribution here is the development of a traffic generator tool that at the same time can provide realistic synthetic traffic, and its modeling framework is extensible for most of the traffic generation libraries and tools. In fact, our current implementations use tow very distinct packet-crafters: \textit{libtins}, a C++ library designed for the implementation of sniffers and traffic generators, and Iperf, a traffic generator commonly used to measure bandwidth.

Out tests performed on the chapter ~\ref{ch:validation} intend to focus on packet-level, flow-level and scaling metrics, as we state on chapter ~\ref{ch:literature-review}. The results were notably good at the flow-level. SIMITAR were able to replicate the flow-cumulative distribution with high accuracy, and with \textit{libtins}, the number of flows as well. The number of flows was larger because it establishes additional connections for signaling and statistics control. On scaling and packet matrics, the results still have to be improved. Iperf as the traffic generator tool, still being limited, has proved to be efficient on replication the scaling characteristics for the Skype traffic. Since it establishes socket connections to generate the traffic, we believe that this fact makes it accurate on replication traffic from applications.

Finally, we created a list of improvements and future works, aiming the improvement of performance on processing time, and packet generation; and the methods to improve the realism of the traffic generated. In the is we believe to overcome the current limitations.
